Practical Optional Types for Clojure

### 2015-07-08 formal-model.tex
edits to sections 3 and 5

\egref{example:getparent-direct-constructor} translates like so.
$$
\clj{(.getParent (new File "a/b"))}
$$
\begin{equation}  \label{eq:unresolved}
  \qquad {\methodexp {\getparent{}} {\newexp {\File{}} {\makestr{a/b}}} {}}
\end{equation}

@@

The expression 
{\extendmultiexp {\e{m}} {\e{v}} {\e{f}}} creates a new multimethod
that extends multimethod \e{m}'s dispatch table, mapping dispatch value
\e{v} to method \e{f}. The typing rule for \defmethodliteral{}
checks \e{m} is a multimethod with dispatch function type \t{d},
then calculates the extra information we know based on the current
dispatch value {\thenprop{\proppp{}}}, which is assumed when checking the method
body.
$$
    \TDefMethod{}
$$
Expression~\ref{eq:hi-defmethoden} checks with \e{m} being of type
$$
{\MultiFntype {\ArrowTwo{\x{}}{\Keyword}{\String}}
              {\ArrowOne{\x{}}{\Keyword}{\Keyword}{\filterset{\topprop{}}{\topprop{}}}{\x{}}}}
$$
with \objectp{} = {\x{}} and \t{v} = \Value{\makekw{en}}. Then {\thenprop{\proppp{}}} = 
{\isprop {\Value{\makekw{en}}}{\x{}}} by
$$
\isacompare{}{\x{}}{\Value{\makekw{en}}}
{\filterset {\isprop {\Value{\makekw{en}}}{\x{}}}{\notprop{\Value{\makekw{en}}}{\x{}}}}
$$
Since \t{} = \Keyword{}, we check the method body like so
$$
\judgement{{\isprop{\Keyword}{\x{}}},{\isprop {\Value{\makekw{en}}}{\x{}}}}
  {\makestr{hello}}
  {\String}{\filterset{\topprop{}}{\topprop{}}}{\emptyobject{}}
$$
Finally from the interface type \t{m}, we know \thenprop{\prop{}} = \elseprop{\prop{}} = \topprop{},
and \object{} = \emptyobject{}, which also agrees with the method body, above.

@@

\subsection{Multimethods and Java}
\subsection{Multimethods and HMaps}

>>>>

\egref{example:getparent-direct-constructor} translates to expression~\ref{eq:unresolved}.
$$
\clj{(.getParent (new File "a/b"))}
$$
\begin{equation}  \label{eq:unresolved}
  \qquad {\methodexp {\getparent{}} {\newexp {\File{}} {\makestr{a/b}}} {}}
\end{equation}

@@

The expression 
{\extendmultiexp {\e{m}} {\e{v}} {\e{f}}} creates a new multimethod
that extends multimethod \e{m}'s dispatch table, mapping dispatch value
\e{v} to method \e{f}. The typing rule for \defmethodliteral{}
checks \e{m} is a multimethod with dispatch function type \t{d},
then calculates the extra information we know based on the current
dispatch value {\thenprop{\proppp{}}}, which is assumed when checking the method
body.
$$
    \TDefMethod{}
$$
Expression~\ref{eq:hi-defmethoden} checks with \e{m} being of type
$$
{\MultiFntype {\ArrowTwo{\x{}}{\Keyword}{\String}}
              {\ArrowOne{\x{}}{\Keyword}{\Keyword}{\filterset{\topprop{}}{\topprop{}}}{\x{}}}}
$$
with \objectp{} = {\x{}} and \t{v} = \Value{\makekw{en}}. Then {\thenprop{\proppp{}}} = 
{\isprop {\Value{\makekw{en}}}{\x{}}} by
$$
\isacompare{}{\x{}}{\Value{\makekw{en}}}
{\filterset {\isprop {\Value{\makekw{en}}}{\x{}}}{\notprop{\Value{\makekw{en}}}{\x{}}}}
$$
Since \t{} = \Keyword{}, we check the method body with
$$
\judgement{{\isprop{\Keyword}{\x{}}},{\isprop {\Value{\makekw{en}}}{\x{}}}}
  {\makestr{hello}}
  {\String}{\filterset{\topprop{}}{\topprop{}}}{\emptyobject{}}
$$
Finally from the interface type \t{m}, we know \thenprop{\prop{}} = \elseprop{\prop{}} = \topprop{},
and \object{} = \emptyobject{}, which also agrees with the method body, above.

@@

\subsection{Proof system}

% checks obvious prop logic, but update is most interesting rule.
